\chapter{Introduction}
\label{ch:intro}

\section{Background of the company}
\label{sec:intro:background}
Founded in 2020, dataTactics GmbH has a clear mission: to empower companies to access, work with, and extract value from their data. By employing agile methodologies, dataTactics enables companies to swiftly deliver products to market and quickly adapt to changing market demands, staying ahead of the competition.

Their open-source approach helps companies avoid vendor lock-in. Since open-source tools are mostly free to use, companies can reduce their software licensing costs and reallocate those budgets to other critical areas, maintaining cost-effective operations. Additionally, their cloud-native approach allows companies to deliver more value to their customers and operate more efficiently. This can potentially reduce overall operational costs by dynamically scaling resources based on demand.

%
% Section: Problem Statement
%
\section{Problem Statement}
\label{sec:intro:problem_statement}
In large environments such as airports, stadiums, and amusement parks, managing incidents and ensuring effective communication can be extremely challenging. Traditionally, staff members use telephones or radios to report issues, a method that is inefficient and prone to delays. This fragmented communication often results in slow response times, miscommunication, and higher operational costs. Additionally, technicians face difficulties in receiving timely and accurate information about technical problems, leading to prolonged downtimes and compromised safety. Ops-Edge addresses these issues by providing a centralized, cloud-based platform that streamlines incident reporting and management, facilitating faster and more effective collaboration among all involved parties.

%
% Section: Internship Roles and Objectives
%
\section{Internship Roles and Objectives}
\label{sec:intro:internship_roles_and_objectives}
During my internship at dataTactics GmbH, I served as a Software Engineer from March 15 to June 15. My primary project was Ops-Edge, a cloud-based application designed to provide a unified reporting system across different operational levels. This project utilizes a Python backend with Flask, and a React frontend leveraging the Mantine framework.

The main objectives of my internship included:

\begin{itemize}
    \item To gain hands-on experience with the technologies and tools used in the development of Ops-Edge.
    \item To enhance my skills in software development, particularly in full-stack development, and to improve my ability to work collaboratively in a team environment.
    \item To understand the day-to-day responsibilities of a software engineer and to explore various aspects of working in a tech company.
    \item To contribute to the development of Ops-Edge by working on both the backend and frontend components, ensuring the system is efficient, reliable, and user-friendly.
    \item To integrate Ops-Edge with external data source such as weather data, traffic data, and other relevant data sources to provide real-time updates and insights.
    \item To ensure that all components are thoroughly tested and integrated seamlessly, maintaining high standards of performance and reliability.
\end{itemize}

Throughout the internship, I focused primarily on the Ops-Edge project. Additionally, I utilized the Fab React toolkit, a library that dataTactics developed to streamline the development process and ensure consistency across projects. This toolkit bootstrapped the project, providing faster development cycles and a more efficient workflow. Notable achievements during my internship included creating the model and frontend UI, adding real-time notification capabilities through Socket.IO, and integrating weather data from an external data source into the application.