\chapter{Learning and Challenges}
\label{ch:learning_challenges}

%
% Section: Key Learnings
%

\section{Key Learnings}
\label{sec:learning_challenges:key_learnings}

My internship at dataTactics GmbH provided me with valuable insights into software development, web development, and working in a tech company. Some of the key learnings from my internship include:

\subsection{Technical skills}
\label{subsec:learning_challenges:technical_skills}

\begin{itemize}
    \item \textbf{Full-stack development:} I gained hands-on experience in full-stack development, working on both the backend and frontend components of the Ops-Edge project. This experience helped me understand the end-to-end development process and the challenges involved in building a complete application.
    \item \textbf{Python and Flask:} I improved my Python skills and learned how to use the Flask framework to build RESTful APIs and web applications. I also improve my knowledge regarding ORM especially in SQLAlchemy.
    \item \textbf{React and Mantine:} I gained experience in building user interfaces using React and the Mantine framework. I learned how to create reusable components, manage state, and handle user interactions in a React application.
    \item \textbf{Socket.IO:} I learned how to use Socket.IO to add real-time communication capabilities to the Ops-Edge application. This allowed me to implement real-time notifications and updates for users.
    \item \textbf{External data integration:} I integrated external data sources such as weather data into the Ops-Edge application to provide real-time weather data (e.g. Frankfurt weather). This experience helped me understand how to work with external APIs and integrate external data into an application.
\end{itemize}

\subsection{Soft skills}
\label{subsec:learning_challenges:soft_skills}

\begin{itemize}
    \item \textbf{Problem-solving:} I developed my problem-solving skills by tackling various technical challenges during the internship. I learned how to analyze problems, identify solutions, and implement them effectively.
    \item \textbf{Time management:} I learned how to manage my time effectively to meet project deadlines and deliver high-quality work. I improved my ability to prioritize tasks, set goals, and stay organized throughout the internship.
    \item \textbf{Adaptability:} I learned how to adapt to new technologies, tools, and working environments quickly. I developed the flexibility to learn new skills and adjust to changing project requirements.
    \item \textbf{Communication:} I improved my communication skills by discussing project requirements with my colleagues, sharing updates on my progress, and seeking feedback on my work.
\end{itemize}

\subsection{Professional development}
\label{subsec:learning_challenges:professional_development}

\begin{itemize}
    \item \textbf{Active updates and task tracking:} I learned how to utilize github projects and issues to track my tasks and updates. I also update my progress daily what was done, what is in progress, and what is next.
    \item \textbf{Software development best practices:} I learned about software development best practices, including code quality, testing, documentation, and version control. I gained insights into how to write clean, maintainable code and follow industry standards.
    \item \textbf{Agile methodologies:} I gained experience working in an agile environment, following agile methodologies such as Kanban Board and deliver incremental updates to the project.
    \item \textbf{Continuous learning:} I developed a growth mindset and a passion for continuous learning. I realized the importance of staying updated with the latest technologies and trends in the software development industry.
\end{itemize}

%
% Section: Challenges Faced
%

\section{Challenges Faced}
\label{sec:learning_challenges:challenges_faced}
% TODO: Add challenges faced during the internship.